---
title: "Assignment HW09"
author: "Julius Mwangi"
date: "July 21, 2018"
output: html_document
---
#1. Harry Porter Cast

## 1a,b

```{r}
library(XML)
webpage<-read_html("http://www.imdb.com/title/tt1201607/fullcredits?ref_=tt_ql_1")
actor<-html_text(html_nodes(webpage, 'span.itemprop'))
character <-html_text(html_nodes(webpage,'.character'))
character <-gsub('[\n]','',character)
character<- gsub('^ +','',character)
character<-gsub('+$', '',character)
character<-gsub(' +', '',character)
cast<-data.frame(actor,character)
head(cast,10)
```

#replace  Mr. Warwirck's  character column with  just  "Griphook  /  Professor  Filius  Flitwick"

```{r}
grep("Warwick",actor)
actor[10]
gsub("Griphook/ProfessorFiliusFlitwick", "Griphook/Professor Filius Flitwick", character)
head(cast,10)
```
##d. Split  the  Actor's  name  into  twocolumns:  FirstName  and Surname.    Keep  in  mind  that  some  actors/actresses  have  middle  names  as  well.    Please  make  sure  that  the  middle  names  are  in  theFirstName  column,  in  addition  to  the  first  name

```{r}
name<- data.frame(actor, character)
library(tidyr)
Names<- extract(name, actor, c("FirstName", "SurName"), "(.*) ([^ ]+)$")
Namesall<-data.frame(Names, character)
head(Names,10)
```
#2. SportsBall (a,b,c)
```{r}
library(XML)

#read the data from esn website
webpage<-readHTMLTable ("http://www.espn.com/nba/team/stats/_/name/sa/san-antonio-spurs", which=2)

# to change dfnames from data frames to vector. Replace data.frame with c 
dfnames <- c("PLAYER","FGM","FGA","FG%","3PM","3PA","3P%","FTM",
"FTA","FT%","2PM","2PA","2P%","PPS","AFG%")
colnames(webpage) <- dfnames
webpage <- webpage[-1 ,]
webpage <- webpage[-16 ,]

# to split PLAYER and rename the two columns "Nam" and "POS"
nampo <- strsplit(as.character(webpage$PLAYER), ",")
Nam <- sapply(nampo, function(x) x[1])
POS <- sapply(nampo, function(x) x[2])
summary(webpage)
```
#d. Create  a  colorful  bar  chart  that  shows  the  *Field Goals Percentage Per Game for  each  person
```{r}
library(ggplot2)
player_details <- data.frame(Nam, POS, webpage[2:length(webpage)])
info_plot <- ggplot(data = player_details , aes(x = player_details$Nam, y = as.numeric(as.character(player_details$FG)))) +geom_bar(stat= "identity", width = 0.5)

```
